Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-05 paper/paper.tex
paper updated
first picture included

    \usepackage{microtype}
    \usepackage{blindtext}

	\usepackage{amsmath}%,amssymb} 
	\usepackage{makeidx}
	\usepackage{amsfonts}
	\usepackage[ansinew]{inputenc}
	\usepackage[usenames,dvipsnames]{pstricks}
	\usepackage{subfigure}
	\usepackage{epsfig}
%	\usepackage{pst-grad} % For gradients
	\usepackage{pst-plot} % For axes
	\usepackage[colorlinks,hyperindex]{hyperref}
	\hypersetup
	{
		colorlinks,%
		citecolor=black,%
		linkcolor=black,%
		urlcolor=black,%
	}

@@

We first lay out the main aspects of our model in a 
partially abstract fashion in the next section.
%rather high-level fashion. 
More details on the actual implementation are then provided in the third
section (or ultimately in the published source
code / supplementary material).
Finally, some of the obtained results are presented and discussed.

@@

Therefore, we optimized $F_C(G)$ using a genetic algorithm, which is inherently
capable of coping with the stochastic fitness function. In each iteration
of the algorithm, a generation $\mathcal{G}_t = \left\{ G_i~|~1\le i\le N\right\}$
of $N$ individuals (Generators) is converted into a new one, $\mathcal{G}_{t+1}$,
according to the following scheme:
\begin{description}
 \item[Evaluation] The fitness $F_i = F_C(G_i)$ of each individual is
     measured using at least 20 samples (and adaptively more if the
     $(F_i)_{1\le i\le N}$ are spaced closely, to at most 100).
 \item[Selection] All individuals are grouped into disjunct pairs for which
     we check which one has the higher fitness. This is repeated $k=10$ times,
     counting the number of wins for each individual. Based thereon we use the
     $p=50\%$ best individuals $\mathcal{G}\Ix{survive}_t$ to build the next
     generation.  By using pair comparisons instead of simple ordering
     according to the fitness, we allow weaker individuals to reach
     the next generation (albeit with low probability), keeping the gene
     pool more diverse.

@@

\paragraph{Choice of Parameters}

\section{Results}
Baseline
gain and feedback tests

@@

\section{Discussion}

>>>>

    \usepackage{microtype}
    \usepackage{blindtext}
    \usepackage{enumitem}

	\usepackage{amsmath}%,amssymb} 
	\usepackage{makeidx}
	\usepackage{amsfonts}
	\usepackage[ansinew]{inputenc}
	\usepackage[usenames,dvipsnames]{pstricks}
	\usepackage{subfigure}
	\usepackage{epsfig}
%	\usepackage{pst-grad} % For gradients
	\usepackage{pst-plot} % For axes
	\usepackage[colorlinks,hyperindex]{hyperref}
    \usepackage{color}
	\hypersetup
	{
		colorlinks,%
		citecolor=black,%
		linkcolor=black,%
		urlcolor=black,%
	}

@@

We first lay out the main aspects of our model in a 
%partially abstract fashion in the next section.
rather high-level overview. 
More details on the actual implementation are then provided in the third
section (or ultimately in the published source
code / supplementary material).
Finally, some of the obtained results are presented and discussed.

@@

Therefore, we optimized $F_C(G)$ using a genetic algorithm, which is inherently
capable of coping with the stochastic fitness function. In each iteration
of the algorithm, a generation $\mathcal{G}_t = \left\{ G_i~|~1\le i\le N\right\}$
of $N$ individuals (Generators) is converted into a new one, $\mathcal{G}_{t+1}$,
according to the following scheme:
\begin{description}[itemsep=1ex, leftmargin=0pt]
 \item[Evaluation] The fitness $F_i = F_C(G_i)$ of each individual is
     measured using at least 20 samples (and adaptively more if the
     $(F_i)_{1\le i\le N}$ are spaced closely, to at most 100).
 \item[Selection] All individuals are grouped into disjunct pairs for which
     we check which one has the higher fitness. This is repeated $k=10$ times,
     counting the number of wins for each individual. Based thereon we use the
     $p=50\%$ best individuals $\mathcal{G}\Ix{survive}_t$ to build the next
     generation.  By using pair comparisons instead of simple ordering
     according to the fitness, we allow weaker individuals to reach
     the next generation (albeit with low probability), keeping the gene
     pool more diverse.

@@

\paragraph{Choice of Parameters}
- $N=100$ fixed, since greater $N$ always increased quality and computational cost
increased quadraticaly to $N$
- Mutation rate

\section{Results}
\subsection{Frequency Dependent Optimizations}
- short description: get feeling for frequency range (by using unoptimized parameters
from the force paper), make optimizations with 3 different challenges: 1) challenges that cover the frequency area completely, challenges that cover low frequencies, and challanges that cover high frequencies, then pick genotypes with high fitness.
\subsection{Topology Optimizations}
Baseline
gain and feedback tests

@@

\begin{figure}
    {\footnotesize\input{pictures/freqrange}}
    \caption{CAPTION TEXT}
    \label{fig:freqrange}
\end{figure}

\section{Discussion}
- Remarks
    * Influence of initial conditions
        -> Degenerated initial population poses major problems (does not
        find same / takes very long to find same parameters as when started
        with diversity).
        -> With broad diversity: often fast convergence -> Gen. Optimizer
        good as optimizing filter, but has hard times to explore new
        parameter regions if no right genotypes are present (especially isolated
        maxima of $F_C$). Solution: Could introduce migrants, that supply
        the gene-pool with underrepresented genotypes.
    * According to experience: maybe not ideal for finding single set of
      parameters but rather for successful parameter-ranges (branches?)

- Problems
    * Many magic parameters scattered in the model that were not examined exhaustively
    * Only few and uncomprehensive number of test / experiments conducted due to the
      computational cost.
    * Test with several other topologies did not yield concrete results,
      only rough tendencies.
    * Influence of statistics: Learning success depends stronger on choice
      of challenges than parameters (partially) -> must be very careful how to
      interpret the results
